Technical Paper Proposal: \\ Placement Algorithms for Heterogenous FPGAs

### 2024-09-10 docs/proposal/proposal.tex
more prop

In modern software development, the process of compiling high-level languages like C++ or Java into executable machine code is highly efficient and streamlined. 
The software toolchains only consist of compilers and scripts and are mostly open source and easy to learn. 
The compilation is where most of the magic happens. The developer can influence a few optimization flags if needed, but for the most part, the developer simply executes the default compiler command. Through multiple stages of lexing, parsing, and optimizations, the compiler takes the developer's program and produces working machine code. All of this happens within milliseconds to seconds, even for large projects.

In the same way that a compiler takes your high-level C++ file and assembles machine code ready to be executed on a CPU, an Electronic Design Automation (EDA) tool takes your high-level Verilog file and produces a hardware configuration in the form of a bitstream, ready to be deployed onto an FPGA or ASIC. In a superficial way, they perform the same task but for different industries. One for software, the other for hardware.

@@

In the FPGA world, the design entry to product pipeline is despairingly complex by comparison. 
First, the design entry. The engineer describes a digital system using a high-level HDL like Verilog or VHDL. 
Then the engineer submits the design entry to an EDA like Vivado or Quartus to perform three stages of automated design. 
These are: synthesis, placement, and routing. and then yap about NP-hardness and massive search space and hellish runtime.

@@

\newpage
\bibliographystyle{ieeetr}
\nocite{*}
\bibliography{
    references/surveys,
    references/rapidwright,
    references/fpga_placement,
    references/vlsi_placement,
}

\end{document}

>>>>

In modern software development, the process of compiling high-level languages like C++ or Java into executable machine code is highly efficient and streamlined. 
The software toolchains only consist of compilers and scripts and are mostly open source and easy to learn. 
The compilation is where most of the magic happens.
Through multiple stages of lexing, parsing, and optimizations, the compiler takes the developer's program and produces working machine code.
The developer can influence a few optimization flags if needed, but for the most part, the developer simply runs the default compiler command and is presented with the final product.
All of this happens within milliseconds to seconds, even for large projects.

In the same way that a compiler takes a high-level C++ file and assembles machine code ready to be executed on a CPU, an Electronic Design Automation (EDA) tool takes a high-level Verilog file and produces a hardware configuration in the form of a bitstream, ready to be deployed onto an FPGA or ASIC. In a superficial way, they perform the same task but for different industries. 
One for software, the other for hardware.

@@

In the FPGA world, the design entry to product pipeline is despairingly complex by comparison. 
First, the design entry. The engineer describes a digital system using a high-level HDL like Verilog or VHDL. 
Then the engineer submits the design entry to an EDA like Vivado or Quartus to perform three stages of automated design. 
These are: synthesis, placement, and routing. 
All three are NP-hard problems.
For even modest designs like binary counters or 8-bit CPUs that utilize a small percentage of the available resources on the FPGA, the EDA will spend a minimum of a couple minutes building the design.
The EDA build time increases exponentially with the scale of the project. 
Projects that utilize 80\% or more of the FPGA's resources may build for hours, and for the high-end devices like Xilinx's Kintex which boast millions of logical elements, can take days.
Sometimes the EDA cannot fit the design onto the device.
Sometimes you step out of the doll-house and the world seems like a heironymous bosch painting.

@@

\newpage
\bibliographystyle{ieeetr}
\nocite{*}
\bibliography{
    references/surveys,
    references/rapidwright,
    references/fpga_placement,
    references/vlsi_placement,
}
\end{document}
